### 2014-10-03 tex/proofs.tex
Macro'd and renamed all the relations and state designations--first pass

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation as defined in
\eqref{eqn:BisimulationForwards} and
\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\ell$ and
$s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
s_\varsigma$, every successor, from either state, $s_\ell
\rightarrow_\ell s_\ell^\prime$ or $s_\varsigma \rightarrow_\varsigma
s_\varsigma^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $s_\ell^\prime \sqsubset s_\varsigma^\prime$.

If the $\varsigma$-relation is considered to be a model of the
$\ell$-relation (i.e., a representation of that machine), then the
representation relation, as a bisimulation, ensures that the
$\varsigma$-relation is complete in that any property that can be
shown in the $\ell$-relation can also be shown in the
$\varsigma$-relation; and further, the representation relation as a
bisimulation ensures that the $\varsigma$-relation is also sound in
that any property that can be shown to hold in the $\varsigma$-relation
can also be shown to hold in the $\ell$-relation.

The proof of the representation relation as a bisimulation reasons
over individual rules in the $\varsigma$-relation to show that for
each rule, the representation relation, $\sqsubset$, exists. The heart
of the representation relation is the homomorphism that maps locations
in one heap to locations in the other heap. The proof reasons over of
each rule and as mentioned previously, and derives from the current
homomorphism in the representation relation for the current states, a
new homomorphism that is sufficient to use in the a new representation
relation that includes the successor states. The proof is constructive
in that it shows how given a valid homomorphism for the current
states, it is possible to derive a new homomorphism that includes
successor states. With such a new homomorphism, it is possible to
state that for the $\varsigma$-relation, when restricted to a specific
rule (i.e., that is the only rule available in the relation), the
representation relation is a bisimulation for that restricted
$\varsigma$-relation. If such a bisimulation exists for all the
individual rules, then it exists for the rules collectively.

There are two slight complications in the proof: first, the field
access rule relies on the $S$-relation that operates on a different
state than then $\varsigma$-relation; and second, constructing the new
homomorphism in the equals-reference rule relies on the incoming heap
being deterministic. The $S$-relation effectively produces
an intermediary state that is the state where uninitialized references
are initialized before the field access actually takes place. In
essence, a state on the left of the $\varsigma$-relation that is a
field access, undergoes a transition in which its heap is changed to
initialize fields. Once the fields are initialized, then the actual
field access takes place. The state with the heap that has the
initialized fields is the intermediary state between the state on the
left of the $\varsigma$-relation and the state on the right of the
$\varsigma$-relation. The proof reasons separately about this
intermediary state to prove that it too is exact.

The equals-reference proof must show that any given reference in the
heap is not able to point to two distinct locations at the same
time. If the incoming heap is able to point to two valid locations at
a given reference at the same time, then the help is
non-deterministic, and it is not possible to construct a valid
homomorphism from the existing homomorphism: which location should be
used in the map? As such, the proof first establishes that the
$\varsigma$-relation preserves determinism when the incoming heap is
deterministic. Once that is shown, the exactness of the equals
reference rule is given.

@@

\begin{lemma}[Bisimulation for $S$-relation]
\label{lem:init}
If $s_s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_s^\prime$ such that $(\cfgnt{L}_s\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rightarrow_S^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
 $$s_s^\prime \cong \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
\end{lemma}

\begin{proof}
In order for a state to be equivalent to a set of lazy states, it must be both sound and complete with respect to the set. We will begin the proof by showing completeness, and then finish by demonstrating soundness.

To show completeness, we must show that any state in the set is represented by $s_s$. The definition of representation requires the both the existence of a homomorphism, and proof that the homomorphism constraint is satisfiable. To show that a homomorphism exits, take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$. By Definition~\ref{representation}, we know $s_\ell = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. Take any state $s_\ell^\prime$ where $s_\ell \rightarrow_I^* s_\ell^\prime$, and state $s_s^\prime$ where $s_s \rightarrow_S^* s_s^\prime$. Note that  state $s_\ell^\prime$ has the form: $s_\ell^\prime = \lp \cfgnt{L}_{\ell^\prime}\ \cfgnt{R}_{\ell^\prime}\ \phi_{\ell^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\ell\  \cfgnt{f}\rp$ such that $\lp l_\ell\  \cfgnt{f}\rp \in \cfgnt{R}_{\ell}^\leftarrow$, and let $l_s = h(l_\ell)$. We may classify $l_\ell$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\ell$, $s_\ell^\prime$, $s_s$, and $s_s^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.

Class 1: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f} ) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.  Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $. In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $s_\ell \rightharpoonup_h s_s$, we may surmise that: 
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$

Class 2: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$. Since $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$, the Summarize rule must have altered this reference. A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_{orig}$. Because $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_{orig}$. Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $, and let $l_{orig} = h(l_\alpha)$. In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f ))$. Let $l_{orig} = h(l_\alpha)$. We can see that by the Summarize rule $ (\phi_b\ l_{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$, so therefore:
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$

Class 3: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) \neq \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$. In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$. By establishing which of these possibilities has happened, we can build $h^\prime$. To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) $. If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\ell}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$. Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_s,f )) $. Now, let $h^\prime(l_\alpha) = l_\beta$. Observe that either way,
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$

Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$

We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\ell^\prime} \in \cfgnt{L}_{\ell^\prime}^\rightarrow$ such that:
$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_{\ell^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\ell^\prime},f )) $$
By Definition~\ref{def:homomorphism} we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.

It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constraint is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

Since the heap constraint is satisfiable, we know that $s_\ell^\prime \sqsubset s_s^\prime $. We have therefore shown that for some summary state $s_s$ and an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$ :
\begin{equation} 
(s_\ell \rightarrow_I^* s_\ell^\prime \wedge s_s \rightarrow_S^* s_s^\prime) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime 
\end{equation}

%may take one of four forms: either the field is already initialized, or the uninitialized field is initialized to a new reference, the null reference, or an alias.
%
%We now show that the following four cases for $s_\ell^*$ are represented in $s_s^*$. For the following cases, let $\rightharpoonup_{h}$ be the homomorphism such that $s_\ell \rightharpoonup_{h} s_s$, let $\cfgnt{l}_\ell = \cfgnt{L}_\ell(\cfgnt{r})$, and let $\cfgnt{l}_s = h(\cfgnt{l}_\ell) $
%
%Case 1: Suppose $\cfgnt{R}_\ell(\cfgnt{l}_\ell) \neq \bot$. In this case, because $s_\ell \rightharpoonup_{h} s_s$, we know that $\cfgnt{R}_s(\cfgnt{l}_s) \neq \bot$. This means that in the Summarize rule, $\cfgnt{l}_s \notin \Lambda$, and therefore, $\cfgnt{R}_s(\cfgnt{l}_s) = \cfgnt{R}_{s^*}(\cfgnt{l}_s) $. By extension, 
%
%Case 2: Suppose the field is uninitialized, and the "new" rule gets executed. We add a new location, so this case is represented.
%
%Case 3: Suppose the field is uninitialized, and the "null" rule gets executed. We add a link to the null location, so this case is represented.
%
%Case 4: Suppose the field is uninitialized, and the "alias" rule gets executed. We add links to all possible aliases, so this case is also represented. In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem. 
%
%%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps. The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive. Mutually exclusive constraints are required because lazy heaps only point to one place at at time. Collectively exhaustive constraints are required to eliminate any other possible heaps. We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is equivalent to that set. Or, we might do this on a case-by-case basis to show that for an arbitrary lazy state, any of it's three possible target states is in the feasible set.
%
%Having demonstrated each of these four cases, we now know that 
%$$s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \} \Rightarrow  s_\ell^* \sqsubset s_s^*$$

>>>>

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation as defined in
\eqref{eqn:BisimulationForwards} and
\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\gse$ and
$s_\sym$, are related in the bisimulation, $s_\gse \sqsubset
s_\sym$, every successor, from either state, $s_\gse
\rgse s_\gse^\prime$ or $s_\sym \rsym
s_\sym^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $s_\gse^\prime \sqsubset s_\sym^\prime$.

If $\rsym$ is considered to be a model of the
$\rgse$ (i.e., a representation of that machine), then the
representation relation, as a bisimulation, ensures that the
$\rsym$ is complete in that any property that can be
shown in states related on $\rgse$ can also be shown in the
$\rsym$; and further, the representation relation as a
bisimulation ensures that the $\rsym$ is also sound in
that any property that can be shown to hold in states related by $\rsym$
can also be shown to hold in the $\rgse$.

The proof of the representation relation as a bisimulation reasons
over individual rules in $\rsym$ to show that for
each rule, the representation relation, $\sqsubset$, exists. The heart
of the representation relation is the homomorphism that maps locations
in one heap to locations in the other heap. The proof reasons over of
each rule and as mentioned previously, and derives from the current
homomorphism in the representation relation for the current states, a
new homomorphism that is sufficient to use in the a new representation
relation that includes the successor states. The proof is constructive
in that it shows how given a valid homomorphism for the current
states, it is possible to derive a new homomorphism that includes
successor states. With such a new homomorphism, it is possible to
state that for $\rsym$, when restricted to a specific
rule (i.e., that is the only rule available in the relation), the
representation relation is a bisimulation for the restricted
$\rsym$. If such a bisimulation exists for all the
individual rules, then it exists for the rules collectively.

There are two slight complications in the proof: first, the field
access rule relies on $\rsum^*$ that operates on a different
state than $\rsym$; and second, constructing the new
homomorphism in the equals-reference rule relies on the incoming heap
being deterministic. The relation $\rsum^*$ effectively produces
an intermediary state that is the state where uninitialized references
are initialized before the field access actually takes place. In
essence, a state on the left of $\rsym$ that is a
field access, undergoes a transition in which its heap is changed to
initialize fields. Once the fields are initialized, then the actual
field access takes place. The state with the heap that has the
initialized fields is the intermediary state between the state on the
left of $\rsym$ and the state on the right of $\rsym$. The proof reasons separately about this
intermediary state to prove that it too is exact.

The equals-reference proof must show that any given reference in the
heap is not able to point to two distinct locations at the same
time. If the incoming heap is able to point to two valid locations at
a given reference at the same time, then the help is
non-deterministic, and it is not possible to construct a valid
homomorphism from the existing homomorphism: which location should be
used in the map? As such, the proof first establishes that
$\rsym$ preserves determinism when the incoming heap is
deterministic. Once that is shown, the exactness of the equals
reference rule is given.

@@

\begin{lemma}[Bisimulation for $S$-relation]
\label{lem:init}
If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
 $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
\end{lemma}

\begin{proof}
In order for a state to be equivalent to a set of GSE states, it must be both sound and complete with respect to the set. We will begin the proof by showing completeness, and then finish by demonstrating soundness.

To show completeness, we must show that any state in the set is represented by $s_\sym$. The definition of representation requires the both the existence of a homomorphism, and proof that the homomorphism constraint is satisfiable. To show that a homomorphism exits, take any GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$. By Definition~\ref{representation}, we know $s_\gse = \lp \cfgnt{L}_\gse\ \cfgnt{R}_\gse\ \phi_\gse\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. Take any state $s_\gse^\prime$ where $s_\gse \rinit^* s_\gse^\prime$, and state $s_\sym^\prime$ where $s_\sym \rsum^* s_\sym^\prime$. Note that  state $s_\gse^\prime$ has the form: $s_\gse^\prime = \lp \cfgnt{L}_{\gse^\prime}\ \cfgnt{R}_{\gse^\prime}\ \phi_{\gse^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\gse\  \cfgnt{f}\rp$ such that $\lp l_\gse\  \cfgnt{f}\rp \in \cfgnt{R}_{\gse}^\leftarrow$, and let $l_\sym = h(l_\gse)$. We may classify $l_\gse$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\gse$, $s_\gse^\prime$, $s_\sym$, and $s_\sym^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.

Class 1: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f} ) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.  Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $. In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $s_\gse \rightharpoonup_h s_\sym$, we may surmise that: 
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$

Class 2: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$. Since $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$, the Summarize rule must have altered this reference. A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_{orig}$. Because $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_{orig}$. Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $, and let $l_{orig} = h(l_\alpha)$. In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f ))$. Let $l_{orig} = h(l_\alpha)$. We can see that by the Summarize rule $ (\phi_b\ l_{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$, so therefore:
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$

Class 3: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) \neq \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$. In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$. By establishing which of these possibilities has happened, we can build $h^\prime$. To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) $. If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\gse}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$. Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_\sym,f )) $. Now, let $h^\prime(l_\alpha) = l_\beta$. Observe that either way,
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$

Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$

We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{\gse^\prime}^\rightarrow$ such that:
$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
By Definition~\ref{def:homomorphism} we know that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.

It remains to show that $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constraint is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

Since the heap constraint is satisfiable, we know that $s_\gse^\prime \sqsubset s_\sym^\prime $. We have therefore shown that for some symbolic state $s_\sym$ and an arbitrary GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$ :
\begin{equation} 
(s_\gse \rinit^* s_\gse^\prime \wedge s_\sym \rsum^* s_\sym^\prime) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime 
\end{equation}

%may take one of four forms: either the field is already initialized, or the uninitialized field is initialized to a new reference, the null reference, or an alias.
%
%We now show that the following four cases for $s_\gse^*$ are represented in $s_\sym^*$. For the following cases, let $\rightharpoonup_{h}$ be the homomorphism such that $s_\gse \rightharpoonup_{h} s_\sym$, let $\cfgnt{l}_\gse = \cfgnt{L}_\gse(\cfgnt{r})$, and let $\cfgnt{l}_\sym = h(\cfgnt{l}_\gse) $
%
%Case 1: Suppose $\cfgnt{R}_\gse(\cfgnt{l}_\gse) \neq \bot$. In this case, because $s_\gse \rightharpoonup_{h} s_\sym$, we know that $\cfgnt{R}_\sym(\cfgnt{l}_\sym) \neq \bot$. This means that in the Summarize rule, $\cfgnt{l}_\sym \notin \Lambda$, and therefore, $\cfgnt{R}_\sym(\cfgnt{l}_\sym) = \cfgnt{R}_{s^*}(\cfgnt{l}_\sym) $. By extension, 
%
%Case 2: Suppose the field is uninitialized, and the "new" rule gets executed. We add a new location, so this case is represented.
%
%Case 3: Suppose the field is uninitialized, and the "null" rule gets executed. We add a link to the null location, so this case is represented.
%
%Case 4: Suppose the field is uninitialized, and the "alias" rule gets executed. We add links to all possible aliases, so this case is also represented. In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem. 
%
%%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps. The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive. Mutually exclusive constraints are required because GSE heaps only point to one place at at time. Collectively exhaustive constraints are required to eliminate any other possible heaps. We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is equivalent to that set. Or, we might do this on a case-by-case basis to show that for an arbitrary GSE state, any of it's three possible target states is in the feasible set.
%
%Having demonstrated each of these four cases, we now know that 
%$$s_\gse^* \in \{\forall s_\gse^\prime | \exists s_\gse \sqsubset s_\sym (s_\gse \rightarrow_I^* s_\gse^\prime)  \} \Rightarrow  s_\gse^* \sqsubset s_\sym^*$$

%Comment:
% there is a flaw in the following argument: we claim that "every reference points to the right place at the right time" However, this statement is misleading. The truth is that the way we've defined representation, we can only guarantee that every reference points to the right place at some right time, not every right time like we imply here. The rest of the argument falls apart unless we can first prove that every reference points to the right place at every right time. So, instead of saying A points to B some time when condition X is true, we need to say that A points to B every time condition X is true. In other words, that condition X implies A points to B. This is easy to prove if we don't introduce new variables into the Heap Condition. However, in this case we certainly do introduce a new variable: it's the new reference that we put into the empty field.
%Flawed argument:
%We now prove the reverse case, that $s_\sym^*$ represents no infeasible states. We modified no references from the previous heap, and did not alter the global invariant. This means that every old reference points to the right place at the right time, and that no old reference points to the wrong place at the wrong time.  Thus, if there is a problem with a reference, it must be with one of the new references we created. Since we have already proved that every reference points to the right place at the right time (WARNING: though the preceding statement may be true, we haven't actually proved it yet. See the above comment), there must be some field that points to the wrong place at the wrong time. Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time". Since the right time is every time due to Theorem~\ref{thm:colex}, this implies that the wrong time is no time.
